---
title: "Project Milestone 2 Resubmission"
format: html
editor: visual
---

## Project Milestone 2

**\# What is the data source?**

-   The data set is from 2023 and came in as csv via GitHub.

**\# How does the dataset relate to the group problem statement and question?**

-   The dataset relate to the group problem statement and question because we are investigating the outbreak in California. The dataset provides information about California residents: such as age, race, and other important aspects of this research.

**\# Document the import process**

-   The way we obtained the data sets were we downloaded it from github into our local disk. From there, then uploaded it onto our repo where we could then use the "read_csv" function to import it into our R.

**\# Identify data types for 5+ data elements/columns/variables:**

-   The five elements we chose are within the ca_pop_2023 data set. We chose county, age category, sex, race, and population size. We did not find that health officer region is useful in our scenario.

**\# Data elements that need cleaning or re-categorization**

-   The only one that needed cleaning into the snake case format was sim_LA. The reason for that is because the names were all in caps. In order to do so, we had to use the function "rename_with(TOLOWER)." The other two data sets were already in snake case, so no cleaning up was needed.

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
ca_pop <- read_csv("/home/rstudio/PH251w-Group/ca_pop_2023.csv")
sim_CA <- read_csv("/home/rstudio/PH251w-Group/sim_novelid_CA.csv")
sim_LA <- read_csv("/home/rstudio/PH251w-Group/sim_novelid_LACounty.csv")
```

```{r}
sim_LA <- sim_LA %>%
  rename_with(tolower)
```

```{r}
str(ca_pop)
str(sim_CA)
str(sim_LA)
```

```{r}
mean(ca_pop$pop)
```

```{r}
median(ca_pop$pop)
```

```{r}
range(ca_pop$pop)
```

```{r}
unique(ca_pop$county)
```

```{r}
unique(ca_pop$race7)
```

```{r}
unique(ca_pop$sex)
```

```{r}
unique(ca_pop$age_cat)
```
