---
title: "Project Milestone 2 Resubmission"
format: html
editor: visual
---

## Project Milestone 2

**\# What is the data source?**

-   The data set is from 2023 and came in as csv via GitHub.

**\# How does the dataset relate to the group problem statement and question?**

-   The dataset relate to the group problem statement and question because we are investigating the outbreak in California. The dataset provides information about California residents: such as age, race, and other important aspects of this research.

**\# Document the import process**

-   The way we obtained the data sets were we downloaded it from github into our local disk. From there, we used the "read.csv" function to import it into our R.

**\# Identify data types for 5+ data elements/columns/variables:**

-   The five elements we chose are within the ca_pop_2023 data set. We chose county, age category, sex, race, and population size. We did not find that health officer region is useful in our scenario.

**\# Data elements that need cleaning or re-categorization**

-   The only one that needed cleaning into the snake case format was sim_LA. The reason for that is because the names were all in caps. In order to do so, we had to use the function "rename_with(TOLOWER)." The other two data sets were already in snake case, so no cleaning up was needed.

\`\`\`{r}

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
